Master thesis problem statement: Keyword search over heterogeneous sources

### 2012-10-11 doc/thesis/latex/literature_review.tex
updated problem definition, solutions and literature review. review to be finished

\textit{PayGo approach}\cite{webscale_paygo}  - there is NO single mediated schema over which users pose queries. Queries are routed to to the relevant sources with help statistical methods that are used to model uncertainty at all levels: queries, mappings and underlying data.

>>>>

\textit{PayGo approach}\cite{webscale_paygo}  - With this approach, 'a system starts with
very few (or inaccurate) semantic mappings and these mappings
are improved over time as deemed necessary'.
% TODO: cite{bootstraping}
there is NO single mediated schema over which users pose queries. Queries are routed to to the relevant sources with help statistical methods that are used to model uncertainty at all levels: queries, mappings and underlying data.
